```{r paper_setup, cache=FALSE, include=FALSE}
library(knitcitations)
```

# PrimerTree: Visualizing polymerase chain reaction primer target alignments for environmental sampling #
# Abstract #
## Summary ##
Design and screening of primers is one of the most critical steps in conducting
any polymerase chain reaction (PCR) analysis.  It is important for the primers
to be both sensitive and specific to the samples of interest.  Prior tools
exist for designing primers based on a template and for identifying potential
target sequences in sequence databases.  However no tool currently exists to
systematically analyze the diversity of the PCR products. PrimerTree is a
package which given a set of primers finds all known targets, and generates and
visualizes a phylogenetic tree of the primer products annotated with the
taxonomic information of the samples.

## Availability ##
primerTree is available as a R package under the GPL-2 license available through
[CRAN](http://cran.r-project.org/web/packages/primerTree/index.html).  Source
code and developmental versions available at <http://www.github.com/jimhester/primerTree>.

## Contact ##
[hesterj@ccf.org](mailto:hesterj@ccf.org)

# Introduction #
TODO

# Implementation #
TODO

# Results and Discussion #
TODO

# Conclusions #
TODO

```{r paper_bibliography, results='asis', echo=F}
bibliography(style='markdown')
```
